Interval Probability for Fuzzy Quantum Theories

### 2016-07-02 prob.tex
prob.tex \subsection{Plan} Add email and comments...

>>>>

\andy{Quantum meeting: the basics of classical and quantum standard
and interval probabilities are becoming clearer (except need clearer
exposition). The key step is the replacement of \textquotedbl{}sum\textquotedbl{}
and \textquotedbl{}=\textquotedbl{} in the rule $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$
by various logical operations on sets instead of actually summing
unit norm partitions of unity in $\mathbb{R}$. What remains is to
determine how the Meyer/Mermin debate plays out for finite precision
or uncertain measurements of events, and its implication for the validity
of the Kochen-Specker theorem, and hence for the validity of Gleason's
theorem. Do we have anything ANALOGOUS to a Gleason theorem for interval
probability quantum mechanics? If so, what are the implications for
Kochen-Specker and Bell analogs for interval probabilities, and what
are the implications for the Meyer/Mermin debate? And if not, what
are the consequences? Finally, given whatever remains of Gleason/Kochen-Specker
for uncertain event measurements, what happens when we redefine \textquotedbl{}sum\textquotedbl{}
yet again for $\ff{p^{2}}$ valued quantum theories (and degenerate
states, and density matrices) to create a non-wrapping extension of
interval probability calculus to Galois fields? (The objective is
to put possible/impossible and its extensions on a solid footing for
DQC, and also to set up a seamless transition back to a continuous
CQC limit that is consistent, while incorporating such issues as the
cost of measurement precision.) }

\yutsung{A mathematical reason why Gleason's theorem should not be
valid in the interval-valued probability quantum mechanics. Every
classical probability measure has a one-to-one correspondence to its
Radon-Nikodym derivative. The Radon-Nikodym theorem extends to Gleason's
theorem in quantum, while the role of Radon-Nikodym derivative is
replaced by the density matrix. If there is no easy Radon-Nikodym
theorem for classical interval-valued probability measure (\cite{GilboaSchmeidler1994}
or other sources. Need verify!), it is natural that there is no easy
Gleason's theorem for quantum interval-valued probability measure...

If Gleason's theorem is not valid, a non-Born quantum probability
measure might exist in reality... If there exists a non-Born quantum
probability measure which cannot correspond to any state vectors,
then what's the post-measurement quantum probability measure of it
after measurement? If the updated post-measurement postulate is strange
enough, then commuting observables may not interchange their measurement
order... And commuting observables is compatible is the fundamental
assumption for the Kochen-Specker theorem, the Bell theorem, and everything\dots{}
If commuting observables becomes non-compatible, everything might
need to be rewritten\dots{} }
